Measurement and Probability in Fuzzy Quantum Theories

### 2016-12-26 prop.tex
prop.tex \section{Quantum Interval-valued Probability Measures} Delete two sentences...
comment

@@

@@

This is the most developed part of our current investigation and is
presented in greater detail than the other proposed activities. It
relies on current unpublished results. As argued in the previous
sections, given fixed finite resources, it is only possible to
estimate the quantum probabilities within an interval of
confidence. It is therefore natural to propose the notion of a
``quantum interval-valued probability measure'' that combines the
definitions of conventional quantum probability measures with
classical interval-probabilities.

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}

@@

\amr{Another: the calculus of probabilities requires all probabilities to
be \emph{coherent}. But given limited resources, a user can only
approximate the probabilities and the approximation may not be
completely coherent in the ideal sense.}

@@

As argued in the previous sections, given fixed finite resources,
it is only possible to estimate the quantum probabilities within an
interval of confidence. It is therefore natural to propose the notion
of a ``quantum interval-valued probability measure'' that combines
the definitions of conventional quantum probability measures with
classical interval-probabilities.
